### 2020-12-30 README.Rmd
Update README.Rmd
Removed word typo
Update doi for BMC Biology submission
update doi description
Ready for review

|                                                                             ![epbmclogo](analysis/data/derived_data/horse_DNA_image.png#style=centerme)

# Single cell resolution landscape of equine peripheral blood mononuclear cells reveals diverse cell types including T-bet<sup>+</sup> B cells.

@@

> Roosheel S. Patel*, Joy E. Tomlinson*, Thomas J. Divers, Gerlinde R. Van de Walle, Brad R. Rosenberg, (2020). *Single cell resolution landscape of equine peripheral blood mononuclear cells reveals diverse cell types including T-bet+ B cells*. BMC Biology <https://doi.org/XXXX>

@@

Session information (computer environment and R/package versions) were used to generate the analyses and figures in the manuscript:

>>>>

|                                                                             ![epbmclogo](analysis/data/derived_data/horse_DNA_image.png#style=centerme)                                                   
# Single cell resolution landscape of equine peripheral blood mononuclear cells reveals diverse cell types including T-bet<sup>+</sup> B cells.

@@

> Roosheel S. Patel*, Joy E. Tomlinson*, Thomas J. Divers, Gerlinde R. Van de Walle, Brad R. Rosenberg, (2020). *Single cell resolution landscape of equine peripheral blood mononuclear cells reveals diverse cell types including T-bet+ B cells*. BMC Biology <DOI pending>

@@

Session information (computer environment and R/package versions) used to generate the analyses and figures in the manuscript:
